---
title: "Palmer Penguins"
author: "Nathan Snell"
date: "3/9/2021"
output: github_document
---

## Abstract

The Palmer Long-Term Ecological Research (LTER) study area is an area west of Antarctica. It is one of the three existing research facilities that the United States has to analyze Antarctic marine ecosystems. One of the organisms investigated by the biologists in this facility is the penguin. Observations of the Chinstrap, Adélie, and Gentoo penguins have been recorded on three islands with various measurements in the size, length, region, sex, stage, etc. The health of penguins is often determined by their size and if they can reproduce efficiently. It is for this reason that I want to determine if there is a significant difference in the size of the penguin species and if they have full clutch sizes. I will use exploratory data analysis to determine this. I plan to compare each species of penguins and the percentage at which they completed their clutch. With this data analysis, I intend to draw conclusions if there is a correlation between species of the penguins and how well they can produce a full clutch size.   

## Introduction

The Palmer Long-Term Ecological Research (LTER) study area is an area west of Antarctica. It is one of the three existing research facilities that the United States has in order to analyze Antarctic marine ecosystems. These Antarctic marine ecosystems include sea ice habitats, oceanography, and bird nesting sites. One of the birds that were examined were the antarctic penguins found on three islands. The three species of penguins that were examined were the Adelie, Gentoo, and Chinstrap penguins. Different statistics of these penguins were taken for determination of age, size, island, sex, reproduction, and isotope concentration. Each of these statistics could be pulled from their website to be analyzed. Of the most interest to most scientists is the result of how well a species can reproduce. The reproduction success rate is measured in many different ways as organisms show different reproduction strategies. The penguins of this region show the strategy of completing their clutch. A clutch is a ground nest made by these penguins. A completed clutch has two eggs in them while an uncompleted clutch would have one or no eggs in the clutch. The likelihood of a completed clutch is determined by many variables. However, the variable that will be explored in this experiment is the species of the penguin. in this experiment, I will compare each of the penguin species to the percentage of completed clutches they have. This will be analyzed using exploratory data analysis.          

## Methods and Materials

### Data Aquisition

1. Data was taken from the Palmer Long Term Ecological Research (LTER) study area in Antarctica. These Datasets were downloaded from given packages on github (Horst, et al., 2020).

2. The available datasets packages found on github were uploaded into R studio (RStudio Team, 2020)   

3. Associated packages were downloaded to run these datasets in Rstudio (Wickham, 2020) (Wickham et al., 2021). 

### Data Preparation

1. The Palmar Penguins datasets was converted into a table and run so all the observations and variables were present. The dataset known as "penguins_raw" was then used for the remainder of the experiment. 

2. The table's labels were then renamed so that the dataset could be used to create graphs and charts without hassle.

3. The body masses of each species was compared for each. island. This was done by graphing the body masses of each species compared to the individual islands.

4. The number of penguins for each species was determined by creating a bar graph. 

5. The number of completed clutches and uncompleted clutches were examined for each species. This was done by creating a stacked bar graph.

6. Body masses of each species were individually analyzed by the frequency of their occurrence. 

## Results

```{r}

library(tidyverse)
library(ggplot2)

library(palmerpenguins)
data(package = 'palmerpenguins')
(penguins)
(penguins_raw)

penguins1 <-(penguins) 

penguins_raw1<-(penguins_raw)

penguins_raw1

##Rename

names(penguins_raw1)

penguins_raw2 <-rename(penguins_raw1,
       clutch_completion =`Clutch Completion`,
       body_mass = `Body Mass (g)`,
       species = Species)
penguins_raw2
```



```{r}
ggplot(data= penguins_raw2) +
 geom_jitter(mapping= aes(x= Island, y= body_mass, color= species))+
   labs(y= "Body Mass (g)")


      

ggplot(data= penguins_raw2)+
   geom_bar(mapping=aes(x= species, fill= clutch_completion ))+
   labs(x= "Species", y= "Frequency", fill="Clutch Completion")+
   theme(
   axis.text=element_text(color= "black"),
   axis.text.x= element_text(angle=10, hjust = 1))

```

## Discussion

## References

 Horst AM, Hill AP, Gorman KB (2020). palmerpenguins: Palmer
#>   Archipelago (Antarctica) penguin data. R package version 0.1.0.
#>   https://allisonhorst.github.io/palmerpenguins/. doi:
#>   10.5281/zenodo.3960218.

Hadley Wickham, Romain François, Lionel Henry and
  Kirill Müller (2021). dplyr: A Grammar of Data
  Manipulation. R package version 1.0.3.
  https://CRAN.R-project.org/package=dplyr

H. Wickham. ggplot2: Elegant Graphics for Data
  Analysis. Springer-Verlag New York, 2016.
  
  RStudio Team (2020). RStudio: Integrated
  Development Environment for R. RStudio, PBC,
  Boston, MA URL http://www.rstudio.com/.

